Maps

### 2020-04-28 ms_8.Rmd
Commit with map error fixed

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)
library(gganimate)
library(patchwork)
library(magick)
library(webshot)
webshot::install_phantomjs()

@@

saveRDS(clean_data, file = "final/my_data.rds")
saveRDS(clean_data, file = "my_data.rds")
saveRDS(clean_data, file = "testing123/my_data.rds")

@@

saveRDS(mwData, file = "final/mwData.rds")

@@

saveRDS(shapefiles, file = "final/shapefiles.rds")
```

@@

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Irrigated Acres"

@@

```{r experimentalModels, eval = FALSE}

@@

ggsave("final/impedu_plot.png", plot = impedu_plot)

# See implement plot (plot2) saved as gif

@@

saveRDS(maleedu_model, file = "final/maleedu_model.rds")

@@

gtsave(data = maleedu_gt, filename = "final/maleedu_gt.png")

@@

ggsave("final/maleedu_plot.png", plot = maleedu_plot)

@@

@@

gtsave(data = cowedu_gt, filename = "final/cowedu_gt.png")

@@

ggsave("final/cowedu_plot.png", plot = cowedu_plot)

@@

```{r farmTrends, eval = FALSE}
# this takes foever--cache it

@@

anim_save("final/plot1a.gif", plot1a)

@@

anim_save("final/plot1b.gif", plot1b)

@@

anim_save("final/plot2.gif", plot2)

@@

anim_save("final/plot3.gif", plot3)

@@

plot4_prepd <- full_join(plot4_prepb, plot4_prepc, by = c("YEAR")) %>%
  select(YEAR, n_pop, n_urban_pop) %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  # convert to long format
  melt(id="YEAR")

@@

plot4 <- as_tibble(plot4_prepd) %>%
  # as.numeric is changing years to numbers 1:7
  mutate(YEAR = as.numeric(YEAR), variable = as.character(variable), 
         value = value/1000) %>%
  ggplot(aes(YEAR, value, color = variable)) +
  geom_line() +
  scale_x_discrete(limits = limits4, labels = labels4) +
  scale_fill_viridis_d(aesthetics = "color", breaks=c("n_urban_pop", "n_pop"), labels = c("Urban", "Rural")) +
  labs(x = "Year",
       y = "Population (in thousands)",
       title = "Midwest Urbanization",
       subtitle = "Rural and urban populations over Time",
       color = "") +
  theme_classic() +
  geom_point(aes(group = seq_along(YEAR))) +
  transition_reveal(YEAR)

anim_save("final/plot4.gif", plot4)
```

@@

# Combined plots using magick

@@

### SHINY FINAL
```{r shiny, eval=FALSE}

# This works

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)

# packages for mapping
library(leaflet)
library(spdplyr)
library(rmapshaper)
library(sf)

# Prep the shapefiles
# Now save the gis data with short names for sake of the shiny app
# hopefully this will work...

x <- readRDS("my_data.rds") %>%
    mutate("Value of Farms" = as.numeric(value_farm), "Average Farm Value" = as.numeric(avg_value_farm), 
           "Value of Implements" = as.numeric(value_implements), 
           "Average Implement Value" = as.numeric(avg_value_implements), 
           "Average Farm Size" = as.numeric(avg_size), "Number of Farms" = as.numeric(n_farm), 
           "Acres of Farmland" = as.numeric(acres_farms), "Irrigated Acres" = as.numeric(acres_irrigated), 
           "Percentage of Farmland Irrigated" = as.numeric(pct_irrigated), "Number of Cows" = as.numeric(cows),
           "Number of Cows per Farm" = as.numeric(cows_per_farm), "Number of Horses" = as.numeric(horses), 
           "Total Population" = as.numeric(pop), "Male Population" = as.numeric(male), 
           "Female Population" = as.numeric(female), "Male Percentage of Population" = as.numeric(pct_male),
           "Total School Enrollment" = as.numeric(enrolled), 
           "Percentage School Enrollment" = as.numeric(pct_enrolled), 
           "Urban Population" = as.numeric(urban_pop), 
           "Percent of Population in Urban Areas" = as.numeric(pct_urban), 
           "Illiterate Population" = as.numeric(illiterate), 
           "Illiteracy Rate" = as.numeric(pct_illiterate)) %>%
    select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, 
           "Value of Farms", "Average Farm Value", "Value of Implements", "Average Implement Value",
           "Average Farm Size", "Number of Farms", "Acres of Farmland", "Irrigated Acres", 
           "Percentage of Farmland Irrigated", "Number of Cows", "Number of Cows per Farm", 
           "Number of Horses", "Total Population", "Male Population", "Female Population", 
           "Male Percentage of Population", "Total School Enrollment", 
           "Percentage School Enrollment", "Urban Population", 
           "Percent of Population in Urban Areas", "Illiterate Population", "Illiteracy Rate")

# Now subset by year
# Really should have saved these as Rds files. Will do that later
Census_1870 <- x %>% filter(YEAR == "1870") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1880 <- x %>% filter(YEAR == "1880") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1890 <- x %>% filter(YEAR == "1890") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1900 <- x %>% filter(YEAR == "1900") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1910 <- x %>% filter(YEAR == "1910") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1920 <- x %>% filter(YEAR == "1920") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1930 <- x %>% filter(YEAR == "1930") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1940 <- x %>% filter(YEAR == "1940") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1950 <- x %>% filter(YEAR == "1950") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1960 <- x %>% filter(YEAR == "1960") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

data_sets <- c("Census_1870", "Census_1880", "Census_1890", "Census_1900", "Census_1910", "Census_1920", "Census_1930", "Census_1940", "Census_1950", "Census_1960")

# Everything above this line should be condensed
#####################

allData <- readRDS("my_data.rds")

# Input

ui <- fluidPage(

    # flatly is a nice theme to make the tabs look put together

    # Application title

    navbarPage("Agriculture and Education in the U.S.", theme = shinytheme("flatly"),

               # remember that tab panel is for what shows up in the tab, and title panel is 
               # for what shows up at the top of the page within the tab

               tabPanel("Intro to Midwestern Agriculture",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),

                        # Generate a row with a sidebar
                        sidebarLayout(

                            # Define the sidebar with one input
                            # comprehensive options:
                            # c("1870" = "1870", "1880" = "1880", "1890" = "1890", "1900" = "1900","1910" = "1910", "1920" = "1920", "1930" = "1930", "1940" = "1940", "1950" = "1950", "1960" = "1960")
                            sidebarPanel(
                                selectInput("Year", "Year:", 
                                            choices=c("1870" = "1870", "1890" = "1890", "1910" = "1910"), 
                                            multiple = TRUE)),
                            helpText("From Great Plains Population and Environment Survey Agricultural and Social & Demographic Data.")
                        ),

                        # Create a spot for the plot
                        mainPanel(
                            tabsetPanel(id = "tabsMain",
                                        tabPanel("Plot",

                                                 # this tells the UI what plot to put

                                                 plotOutput("agPlot")  
                                        )))),
               tabPanel("Models",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),
                        p("Make some models! (See notes)"),
                        gt_output("model1")
               ),

               tabPanel("Maps",
                        titlePanel("Midwest Map Explorer"),
                        p("For best results, view in fullscreen mode."),
                        p("Maps may take up to 30 seconds to load...but they're worth it!"),
                   mainPanel(
                         tabsetPanel(id = "tabsMain",
                                                     tabPanel("Map",
                                                              pageWithSidebar(

                                                                  headerPanel(""),

                                                                  sidebarPanel(
                                                                      uiOutput("choose_dataset"),

                                                                      uiOutput("choose_columns"),
                                                                      br(),
                                                                  ),
                                         mainPanel(leafletOutput("map1"))
                                     )),
                                     tabPanel("Interesting Observations",
                                              # Don't write in the first p()
                                              # Looks bad
                                              p(""),
                                              p("Write some stuff!")))
                                 )),

               tabPanel("About",

                        # Give the page a title
                        titlePanel("About this project"),
                        p("My name is Julia Englebert. I am a senior at Harvard College studying Near Eastern Languages and Civilizations with a secondary field in Ethnicity, Migration, and Rights. Some of my academic interests include the history and future of Midwestern agriculture, and the role of data science in shaping social policy."),
                        br(),
                        p("This project uses historical census and American Community Survey (ACS) data to explore correlations between agriculture and education in the Midwestern United States. By joining the two datasets, the former containing agricultural data and the later containing demographic data, I was able to look at the impact of farming, land value, crop value, and more on education in Midwestern communities over the course of a century. I chose this particular time range in part because of the data that was available to me, and in part due to the economic, industrial, and education policy changes that ocurred from 1870 to 1960. My data is sourced from the IPUMS National Historical Geographic Information System (NHGIS) at nhgis.org. IPUMS provides census data from around the world, but my project focuses specifically on the United States from 1870 to 1960. All datasets and gis files used for this project can be downloaded from the NHGIS Data Finder:"),
                        p(a(href="https://data2.nhgis.org/main", "NHGIS Data Finder")),
                        br(),
                        p("To see more of my work, please visit my Github account:"),
                        p(a(href="https://github.com/julia-englebert", "Julia Englebert")),
                        br(),
                        titlePanel("Citations"),
                        p("Steven Manson, Jonathan Schroeder, David Van Riper, and Steven Ruggles. IPUMS National Historical Geographic Information System: Version 14.0 [Database]. Minneapolis, MN: IPUMS. 2019. http://doi.org/10.18128/D050.V14.0"),
                        p("The College of William and Mary and the Minnesota Population Center. School Attendance Boundary Information System (SABINS): Version 1.0. Minneapolis, MN: University of Minnesota 2011.")
               )
               )
    )

# use plotly to allow hover text to appear on plots, giving more info about the point

server <- (function(input, output, session) {

    # Fill in the spot we created for a plot
    output$agPlot <- renderPlot({

        # Render a plot
        allData %>%
            filter(YEAR %in% input$Year) %>%
            mutate(YEAR = as.factor(YEAR)) %>%
            group_by(YEAR) %>%
            ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
            geom_point(alpha = 0.1) +
            geom_smooth(method = "lm", se = FALSE) +
            scale_color_viridis_d() +
            ylim(0, 45) +
            scale_x_log10(labels = comma) +
            labs(title = "Cows and Education",
                 subtitle = "Relationship between the number of cows per farm\nand school enrollment, by county",
                 x = "Average Cows per Farm",
                 y = "Percent of Population Enrolled in School") +
            theme_classic()
    })

    output$choose_dataset <- renderUI({
        selectInput("dataset", "Choose Census Year:", as.list(data_sets))
    })

    # Check boxes
    output$choose_columns <- renderUI({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set with the appropriate name
        dat <- get(input$dataset)

        # Get rid of "YEAR" and "STATE" so that users don't pick them and make senseless maps

        colnames1 <- names(dat)
        colnames <- colnames1[!colnames1 %in% "YEAR" & !colnames1 %in% "STATE"]

        # Create the dropdown menu and select all columns by default
        selectInput("columns", "Choose Variable:", 
                    choices  = colnames)
    })

    # Map output
    output$map1 <- renderLeaflet({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set
        dat <- get(input$dataset)

        # Make sure columns are correct for data set (when data set changes, the
        # columns will initially be for the previous data set)
        if (is.null(input$columns) || !(input$columns %in% names(dat)))
            return()

        year <- dat %>% slice(1) %>% pull(YEAR)

        # Keep the selected columns
        dat <- dat[, input$columns, drop = FALSE]

        myvar <- input$columns

    })

    output$model1 <- render_gt({

        # experimental model

        model1

    })
})

# Run the application

shinyApp(ui = ui, server = server)

# Ignore

```{r ignore, eval=FALSE}
data1870a <- as_tibble(read.csv("raw-data/nhgis0002_csv/nhgis0002_ds16_1870_county.csv")) %>%
  mutate(GISJOIN = as.character(GISJOIN), STATE = as.character(STATE), COUNTY = as.character(COUNTY), 
         AREANAME = as.character(AREANAME))

```{r}
allData_inflated <- as_tibble(bind_rows(data1870j, data1880j, data1890j, 
                       data1900j, data1910j, data1920j, data1930j, data1940j, data1950j, data1960j)) %>%
  mutate(pct_male = male/pop*100, avg_value_farm = value_farm/n_farm, cows_per_farm = cows_per_person, 
         avg_value_implements = value_implements/n_farm, pct_urban = ifelse(pct_urban > 100, NA, pct_urban)) %>%

x <- left_join(allData_inflated, inflation, by = c("YEAR" = "year")) %>%
  # Use the multiplier column to adjust for inflation
  mutate(value_farm = value_farm*multiplier, value_implements = value_implements*multiplier) %>%
  mutate(avg_value_farm = value_farm/n_farm, avg_value_implements = value_implements/n_farm) %>%
  mutate("Value of Farms" = as.numeric(value_farm), "Average Farm Value" = as.numeric(avg_value_farm), 
         "Value of Implements" = as.numeric(value_implements), 
         "Average Implement Value" = as.numeric(avg_value_implements), 
         "Average Farm Size" = as.numeric(avg_size), "Number of Farms" = as.numeric(n_farm), 
         "Acres of Farmland" = as.numeric(acres_farms), "Irrigated Acres" = as.numeric(acres_irrigated), 
         "Percentage of Farmland Irrigated" = as.numeric(pct_irrigated), "Number of Cows" = as.numeric(cows),
         "Number of Cows per Farm" = as.numeric(cows_per_farm), "Number of Horses" = as.numeric(horses), 
         "Total Population" = as.numeric(pop), "Male Population" = as.numeric(male), 
         "Female Population" = as.numeric(female), "Male Percentage of Population" = as.numeric(pct_male),
         "Total School Enrollment" = as.numeric(enrolled), 
         "Percentage School Enrollment" = as.numeric(pct_enrolled), 
         "Urban Population" = as.numeric(urban_pop), 
         "Percent of Population in Urban Areas" = as.numeric(pct_urban), 
         "Illiterate Population" = as.numeric(illiterate), 
         "Illiteracy Rate" = as.numeric(pct_illiterate)) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, 
         "Value of Farms", "Average Farm Value", "Value of Implements", "Average Implement Value",
                   "Average Farm Size", "Number of Farms", "Acres of Farmland", "Irrigated Acres", 
                   "Percentage of Farmland Irrigated", "Number of Cows", "Number of Cows per Farm", 
                   "Number of Horses", "Total Population", "Male Population", "Female Population", 
                   "Male Percentage of Population", "Total School Enrollment", 
                   "Percentage School Enrollment", "Urban Population", 
                   "Percent of Population in Urban Areas", "Illiterate Population", "Illiteracy Rate")

```{r}
Census_1870 <- x %>% filter(YEAR == "1870") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1880 <- x %>% filter(YEAR == "1880") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1890 <- x %>% filter(YEAR == "1890") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1900 <- x %>% filter(YEAR == "1900") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1910 <- x %>% filter(YEAR == "1910") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1920 <- x %>% filter(YEAR == "1920") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1930 <- x %>% filter(YEAR == "1930") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1940 <- x %>% filter(YEAR == "1940") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1950 <- x %>% filter(YEAR == "1950") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

Census_1960 <- x %>% filter(YEAR == "1960") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

saveRDS(Census_1870, file = "final/1870.rds")
saveRDS(Census_1880, file = "final/1880.rds")
saveRDS(Census_1890, file = "final/1890.rds")
saveRDS(Census_1900, file = "final/1900.rds")
saveRDS(Census_1910, file = "final/1910.rds")
saveRDS(Census_1920, file = "final/1920.rds")
saveRDS(Census_1930, file = "final/1930.rds")
saveRDS(Census_1940, file = "final/1940.rds")
saveRDS(Census_1950, file = "final/1950.rds")
saveRDS(Census_1960, file = "final/1960.rds")

# Working App

```{r workingApp}
# START THE APP

# Input

ui <- fluidPage(

    # flatly is a nice theme to make the tabs look put together

    # Application title

    navbarPage("Agriculture and Education in the U.S.", theme = shinytheme("flatly"),

               # remember that tab panel is for what shows up in the tab, and title panel is 
               # for what shows up at the top of the page within the tab

               tabPanel("Intro to Midwestern Agriculture",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),

                        # Generate a row with a sidebar
                        sidebarLayout(

                            # Define the sidebar with one input
                            # comprehensive options:
                            # c("1870" = "1870", "1880" = "1880", "1890" = "1890", "1900" = "1900","1910" = "1910", "1920" = "1920", "1930" = "1930", "1940" = "1940", "1950" = "1950", "1960" = "1960")
                            sidebarPanel(
                                selectInput("Year", "Year:", 
                                            choices=c("1870" = "1870", "1890" = "1890", "1910" = "1910"), 
                                            multiple = TRUE)),
                            helpText("From Great Plains Population and Environment Survey Agricultural and Social & Demographic Data.")
                        ),

                        # Create a spot for the plot
                        mainPanel(
                            tabsetPanel(id = "tabsMain",
                                        tabPanel("Plot",

                                                 # this tells the UI what plot to put

                                                 plotOutput("agPlot")
                                        )))),
               tabPanel("Models",

                        # Give the page a title
                        titlePanel("Relationship Between Farm Value and Education, by County"),
                        p("Make some models! (See notes)"),
                        gt_output("model1")
               ),

               tabPanel("Maps",
                        titlePanel("Midwest Map Explorer"),
                        p("For best results, view in fullscreen mode."),
                        p("Maps may take up to 30 seconds to load...but they're worth it!"),
                                sidebarLayout(

                                      sidebarPanel(
                                            uiOutput("choose_dataset"),
                                            uiOutput("choose_columns"),
                                            uiOutput("choose_columns2"),
                                                                      br(),
                                                                  ),
                                         mainPanel(leafletOutput("map1"),
                                                   leafletOutput("map2"))
                                     )),

               tabPanel("About",

                        # Give the page a title
                        titlePanel("About this project"),
                        p("My name is Julia Englebert. I am a senior at Harvard College studying Near Eastern Languages and Civilizations with a secondary field in Ethnicity, Migration, and Rights. Some of my academic interests include the history and future of Midwestern agriculture, and the role of data science in shaping social policy."),
                        br(),
                        p("This project uses historical census and American Community Survey (ACS) data to explore correlations between agriculture and education in the Midwestern United States. By joining the two datasets, the former containing agricultural data and the later containing demographic data, I was able to look at the impact of farming, land value, crop value, and more on education in Midwestern communities over the course of a century. I chose this particular time range in part because of the data that was available to me, and in part due to the economic, industrial, and education policy changes that ocurred from 1870 to 1960. My data is sourced from the IPUMS National Historical Geographic Information System (NHGIS) at nhgis.org. IPUMS provides census data from around the world, but my project focuses specifically on the United States from 1870 to 1960. All datasets and gis files used for this project can be downloaded from the NHGIS Data Finder:"),
                        p(a(href="https://data2.nhgis.org/main", "NHGIS Data Finder")),
                        br(),
                        p("To see more of my work, please visit my Github account:"),
                        p(a(href="https://github.com/julia-englebert", "Julia Englebert")),
                        br(),
                        titlePanel("Citations"),
                        p("Steven Manson, Jonathan Schroeder, David Van Riper, and Steven Ruggles. IPUMS National Historical Geographic Information System: Version 14.0 [Database]. Minneapolis, MN: IPUMS. 2019. http://doi.org/10.18128/D050.V14.0"),
                        p("The College of William and Mary and the Minnesota Population Center. School Attendance Boundary Information System (SABINS): Version 1.0. Minneapolis, MN: University of Minnesota 2011.")
               )
               )
    )

# use plotly to allow hover text to appear on plots, giving more info about the point

server <- (function(input, output, session) {

    # Fill in the spot we created for a plot
    output$agPlot <- renderPlot({

        # Render a plot
        allData %>%
            filter(YEAR %in% input$Year) %>%
            mutate(YEAR = as.factor(YEAR)) %>%
            group_by(YEAR) %>%
            ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
            geom_point(alpha = 0.1) +
            geom_smooth(method = "lm", se = FALSE) +
            scale_color_viridis_d() +
            ylim(0, 45) +
            scale_x_log10(labels = comma) +
            labs(title = "Cows and Education",
                 subtitle = "Relationship between the number of cows per farm\nand school enrollment, by county",
                 x = "Average Cows per Farm",
                 y = "Percent of Population Enrolled in School") +
            theme_classic()
    })

    output$choose_dataset <- renderUI({
        selectInput("dataset", "Choose Census Year:", as.list(data_sets))
    })

    # Check boxes
    output$choose_columns <- renderUI({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set with the appropriate name
        dat <- get(input$dataset)

        # Get rid of "YEAR" and "STATE" so that users don't pick them and make senseless maps

        colnames1 <- names(dat)
        colnames <- colnames1[!colnames1 %in% "YEAR" & !colnames1 %in% "STATE"]

        # Create the dropdown menu and select all columns by default
        selectizeInput("columns", "Choose Variable:", 
                    choices  = colnames)
    })

    # Map output
    output$map1 <- renderLeaflet({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set
        dat <- get(input$dataset)

        # Make sure columns are correct for data set (when data set changes, the
        # columns will initially be for the previous data set)
        if (is.null(input$columns) || !(input$columns %in% names(dat)))
            return()

        year <- dat %>% slice(1) %>% pull(YEAR)

        # Keep the selected columns
        dat <- dat[, input$columns, drop = FALSE]

        myvar <- input$columns

    })

    # map2 dropdown menu
    output$choose_columns2 <- renderUI({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set with the appropriate name
        dat <- get(input$dataset)

        # Get rid of "YEAR" and "STATE" so that users don't pick them and make senseless maps

        colnames1 <- names(dat)
        colnames <- colnames1[!colnames1 %in% "YEAR" & !colnames1 %in% "STATE"]

        # Create the dropdown menu and select all columns by default
        selectizeInput("columns2", "Choose Variable to Compare:", 
                    choices  = colnames,
                    options = list(
                        placeholder = 'Variables...',
                        onInitialize = I('function() { this.setValue(""); }')))
    })

    output$map2 <- renderLeaflet({
        # If missing input, return to avoid error later in function
        if(is.null(input$dataset))
            return()

        # Get the data set
        dat <- get(input$dataset)

        # Make sure columns are correct for data set (when data set changes, the
        # columns will initially be for the previous data set)
        if (is.null(input$columns2) || !(input$columns2 %in% names(dat)))
            return()

        year <- dat %>% slice(1) %>% pull(YEAR)

        # Keep the selected columns
        dat <- dat[, input$columns2, drop = FALSE]

        myvar <- input$columns2

    })

    output$model1 <- render_gt({

        # experimental model

        model1

    })
})

# Run the application

shinyApp(ui = ui, server = server)

>>>>

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
#library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)
library(gganimate)
library(patchwork)
library(magick)
library(webshot)
webshot::install_phantomjs()

@@

# saveRDS(clean_data, file = "final/my_data.rds")
saveRDS(clean_data, file = "my_data.rds")
saveRDS(clean_data, file = "testing123/my_data.rds")

@@

#saveRDS(mwData, file = "final/mwData.rds")

@@

#saveRDS(shapefiles, file = "final/shapefiles.rds")
```

@@

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Value of Farms"

@@

```{r experimentalModels, cache = TRUE}

@@

#ggsave("final/impedu_plot.png", plot = impedu_plot)

# See implement plot (plot2) saved as gif
# also use cowedu model

@@

#saveRDS(maleedu_model, file = "final/maleedu_model.rds")

@@

#gtsave(data = maleedu_gt, filename = "final/maleedu_gt.png")

@@

#ggsave("final/maleedu_plot.png", plot = maleedu_plot)

cows_size_model <- allData %>%
  select(YEAR, pct_enrolled, cows_per_farm, avg_size) %>%
  na.omit() %>%
  lm(pct_enrolled ~ cows_per_farm*avg_size, data = .) %>%
  tidy(conf.int = TRUE)

#saveRDS(cows_size_model, "final/cows_size_model.rds")

@@

#saveRDS(cowedu_model, "final/cowedu_model.rds")

@@

#gtsave(data = cowedu_gt, filename = "final/cowedu_gt.png")

@@

#ggsave("final/cowedu_plot.png", plot = cowedu_plot)

@@

```{r farmTrends, cache=TRUE}
# this takes foever--cache it

@@

#anim_save("final/plot1a.gif", plot1a)

@@

#anim_save("final/plot1b.gif", plot1b)

@@

#anim_save("final/plot2.gif", plot2)

@@

#anim_save("final/plot3.gif", plot3)

@@

# I was having trouble with the foreign package, so I commented out all code that requires it

#plot4_prepd <- full_join(plot4_prepb, plot4_prepc, by = c("YEAR")) %>%
  #select(YEAR, n_pop, n_urban_pop) %>%
  #mutate(YEAR = as.factor(YEAR)) %>%
  # convert to long format
  #melt(id="YEAR")

@@

#plot4 <- as_tibble(plot4_prepd) %>%
  # as.numeric is changing years to numbers 1:7
  #mutate(YEAR = as.numeric(YEAR), variable = as.character(variable), 
         #value = value/1000) %>%
  #ggplot(aes(YEAR, value, color = variable)) +
  #geom_line() +
  #scale_x_discrete(limits = limits4, labels = labels4) +
  #scale_fill_viridis_d(aesthetics = "color", breaks=c("n_urban_pop", "n_pop"), labels = c("Urban", "Rural")) +
  #labs(x = "Year",
       #y = "Population (in thousands)",
       #title = "Midwest Urbanization",
       #subtitle = "Rural and urban populations over Time",
       #color = "") +
  #theme_classic() +
  #geom_point(aes(group = seq_along(YEAR))) +
  #transition_reveal(YEAR)

#anim_save("final/plot4.gif", plot4)
```

# magick code

@@

```
# Combined plots using magick

@@
